---
title: "Quantum Assessment"
author: "Freddy Drennan"
date: "3/4/2019"
output: html_document
resource_files:
- daily_data.rda
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## Recommended Packages 
```{r}
library(tidyverse)
library(ggplot2)
library(lpSolve)
```

# The Advertising Problem

You are running an advertising campaign with Facebook and have data available to make decisions about the allocation of your budget. You are tasked to allocate $500 dollars of budget among three advertisments which have historical performance data by writing a linear program. 

Data Available from February.

+ $s_n$ - Dollars spent for advertisements in the prior month for advertisement $n$. Called `amount_spent`.
+ $i_n$ - Impressions obtained with $s$ dollars in the prior month for advertisement $n$. Called `impressions_obtained`.
+ $c_n$ - Clicks obtained with $s$ dollars in the prior month for advertisement $n$. Called `clicks_obtained`.
+ $k_n$ - The Key Performance Indicator: $\frac{i_n}{s_n}$ 
+ $x_n$ - Budgets for the new month. Your decision variables.

You have 500 dollars to spend this month and three advertisments, while maximizing impressions. The budget allocated to each advertisement is $x_1...x_3$ respectively. 

$$
\begin{align}
max\;\;\;\;\;\;                &  x^T k\\
s.t.\;\;\;\;\;\;               & \:\: \\
                               & \sum_{i=1}^n x_i = 500 \\
                               & x_i >= 25 \:\; \forall\;\;i\\
                               & x_1 - x_2 >= 0 \\
                               & x_3 + x_2 <= 400
\end{align}
$$

The data below is available for your decision making. 

```{r, message=FALSE, warning=FALSE}
advertisement_data <- tibble(
  advertisement_name   = paste0("Advertisement: ", 1:3),
  amount_spent         = c(100, 125, 200),
  impressions_obtained = c(1000, 1530, 105),
  clicks_obtained      = c(250, 350, 600)
)

advertisement_data
```


## Bonus 1:
Add a constraint to keep expected clicks above 1350

## Bonus 2:
Add a constraint to force $x_3$ to always receive at least thirty percent of the total budget allocated to $x_2$ and $x_3$. 

For example, if the sum of advertisment 2 and 3 is 250 dollars, then $250 = x_2 + x_3$ and $x_3 >= .3 (x_2 + x_3)$


EDA: Denver Crime Data
================

Please use the included data in `/denver-crime-data` to answer the
questions that follow. Be sure to push back to this repo any and all
write-up, code, plots, etc., that you used in your analysis.

1.  Are they any alarming or reassuring trends in Denver crime that you
    see?
2.  Do you see any patterns in Denver crime related to neiborhood or
    time-of-day?
3.  What other intersting insight(s) have you discovered about Denver
    crime?



