---
title: "Quantum Assessment"
author: "Freddy Drennan"
date: "3/4/2019"
output: html_document
resource_files:
- daily_data.rda
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# The Birthday Problem

Assumptions:

1. Birthdays are equally likely between Jan 1 and Dec 31. 
2. Leap years are ignored
3. $n$: people are in a room
4. $p$: the probability that at least two people in the room share a birthday

Using ggplot, display the value of $p$ against $n$. 

```{r}
library(tidyverse)
```


# The Advertising Problem

You are running an advertising campaign with Facebook and have data available to make decisions about the allocation of your budget. You are tasked to allocate $500 dollars of budget among three advertisments which have historical performance data by writing a linear program. 

Data Available from February.

+ $s_n$ - Dollars spent for advertisements in the prior month for advertisement $n$. Called `amount_spent`.
+ $i_n$ - Impressions obtained with $s$ dollars in the prior month for advertisement $n$. Called `impressions_obtained`.
+ $c_n$ - Clicks obtained with $s$ dollars in the prior month for advertisement $n$. Called `clicks_obtained`.
+ $k_n$ - The Key Performance Indicator: $\frac{i_n}{s_n}$ 
+ $x_n$ - Budgets for the new month. Your decision variables.

You have 500 dollars to spend this month and three advertisments, while maximizing impressions. The budget allocated to each advertisement is $x_1...x_3$ respectively. 

$$
\begin{align}
max\;\;\;\;\;\;                &  x^T k\\
s.t.\;\;\;\;\;\;               & \:\: \\
                               & \sum_{i=1}^n x_i = 500 \\
                               & x_i >= 25 \:\; \forall\;\;i\\
                               & x_1 - x_2 >= 0 \\
                               & x_3 + x_2 <= 400
\end{align}
$$

The data below is available for your decision making. 

```{r, message=FALSE, warning=FALSE}
advertisement_data <- tibble(
  advertisement_name   = paste0("Advertisement: ", 1:3),
  amount_spent         = c(100, 125, 200),
  impressions_obtained = c(1000, 1530, 105),
  clicks_obtained      = c(250, 350, 600)
)

advertisement_data
```


## Bonus 1:
Add a constraint to keep expected clicks above 1350

## Bonus 2:
Add a constraint to force $x_3$ to always receive at least thirty percent of the total budget allocated to $x_2$ and $x_3$. 

For example, if the sum of advertisment 2 and 3 is 250 dollars, then $250 = x_2 + x_3$ and $x_3 >= .3 (x_2 + x_3)$


# EDA

Take the file from the repo called `daily_data.rda` and do an EDA. What do you find? The lowest level of an advertisment is an adgroup id. 

$$
\text{Adgroup Id} \subset\text{Campaign Id} \subset\text{Advertiser Id} \subset\text{LP Id}
$$

